Make_mash_U_hyp

### 2020-07-09 R/Make_mash_U_hyp.Rmd
specify Uhyp as matrices

  Ugulfhyp <- list.append(Ugulfhyp, Ugulf1 = Ugulf1)
  Umidwhyp <- list.append(Umidwhyp, Umidw1 = Umidw1)
  names(Ugulfhyp)[i] <- names(Ureturn)[i]
  names(Umidwhyp)[i] <- names(Ureturn)[i]
}
str(Umidwhyp)
write_rds(Ugulfhyp, path = file.path(path, "U_hyp_gulf_1phe.rds"))
write_rds(Umidwhyp, path = file.path(path, "U_hyp_midw_1phe.rds"))
```

```{r}
path <- file.path("~", "Github", "pvdiv-phenology-gxe", "analysis", 
                       "gwas", "GDD", "Uhyp")
numSNPs <- 20000
suffix = "midwest_uhyp1"
Umidwhyp <- read_rds(path = file.path(path, "U_hyp_midw_1phe.rds"))

m <- mash_standard_run(path = path, numSNPs = numSNPs, U_hyp = Umidwhyp, 
                       suffix = suffix, saveoutput = TRUE)
```

>>>>

  Ugulfhyp <- list.append(Ugulfhyp, Ugulf1 = as.matrix(Ugulf1))
  Umidwhyp <- list.append(Umidwhyp, Umidw1 = as.matrix(Umidw1))
  names(Ugulfhyp)[i] <- names(Ureturn)[i]
  names(Umidwhyp)[i] <- names(Ureturn)[i]
}
str(Umidwhyp)
is.matrix(Umidwhyp$U_GR50)
isSymmetric(Umidwhyp$U_GR50)
write_rds(Ugulfhyp, path = file.path(path, "U_hyp_gulf_1phe.rds"))
write_rds(Umidwhyp, path = file.path(path, "U_hyp_midw_1phe.rds"))
```

```{r}
path <- file.path("~", "Github", "pvdiv-phenology-gxe", "analysis", 
                       "gwas", "GDD", "Uhyp")
numSNPs <- 20000
suffix = "midwest_uhyp1"
Umidwhyp <- read_rds(path = file.path(path, "U_hyp_midw_1phe.rds"))
Udist <- Umidwhyp$U_dist

m <- mash_standard_run(path = path, numSNPs = numSNPs, U_hyp = Udist, 
                       suffix = suffix, saveoutput = TRUE)

m <- mash_standard_run(path = path, numSNPs = numSNPs, U_hyp = Umidwhyp, 
                       suffix = suffix, saveoutput = TRUE)
```
Error in mashr::mash_set_data(Bhat_random, Shat_random) :
  Shat cannot contain NaN/Inf values
  problem for midwest...

U_hyp must be matrices. They must be symmetric, in the same order as Bhat etc, and with the same # rows and cols as Bhat etc.

```{r}
path <- file.path("~", "Github", "pvdiv-phenology-gxe", "analysis", 
                       "gwas", "GDD", "Uhyp")
numSNPs <- 30000
suffix = "gulf_uhyp1"
Ugulfhyp <- read_rds(path = file.path(path, "U_hyp_gulf_1phe.rds"))
Udistg <- Ugulfhyp$U_dist
U_h1 <- list(Udist = as.matrix(Udistg))
isSymmetric(U_h1$Udist)
typeof(Udistg)

U_ed <- file.path(path, "Mash_data_driven_covariances_30000_gulf_uhyp1.rds")

m <- mash_standard_run(path = path, numSNPs = numSNPs, U_ed = U_ed,
                       U_hyp = U_h1, suffix = suffix, saveoutput = TRUE)
```

```{r}
path <- file.path("~", "Github", "pvdiv-phenology-gxe", "analysis", 
                       "gwas", "GDD", "Uhyp")
m <- readRDS(file.path(path, "Strong_Effects30000SNPs_gulf_uhyp1.rds"))
suffix = "gulf_uhyp1"
mash_plot_covar(m, saveoutput = TRUE, suffix = suffix)
mash_plot_Ulist(m, range = get_U_by_mass(m), saveoutput = TRUE, 
                  suffix = suffix)
mash_plot_sig_by_condition(m, saveoutput = TRUE, suffix = suffix)
mash_plot_pairwise_sharing(m, saveoutput = TRUE, suffix = suffix)
mash_plot_effects(m, n = 1, saveoutput = TRUE, suffix = suffix)
mash_plot_effects(m, n = 2, saveoutput = TRUE, suffix = suffix)
mash_plot_effects(m, n = 8)

mash_plot_manhattan_by_condition(m, saveoutput = TRUE, suffix = suffix)
```
